Fig2: Candidate genes

### 2020-04-17 analysis/figure-2.Rmd
smaller points

  p <- candidatevsd %>%
    filter(tissue == whichtissue,
          gene %in% whichgenes) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    mutate(treatmentNum = as.numeric(treatment)) %>%
    ggplot(aes(x = treatmentNum, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    #geom_smooth(aes(color = sex)) +
    geom_jitter(size = 0.5, aes(color = sex)) +
    facet_grid(gene~sex, scales = "free") +
    scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9),
                       labels = charlevels) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          strip.text.y = element_text(face = "italic"),
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(subtitle = whichtissue, 
         y = "gene expression (variance stabilized)",
         x = "Parental Care Stage") 
  return(p)
}

>>>>

  p <- candidatevsd %>%
    filter(tissue == whichtissue,
          gene %in% whichgenes) %>%
    mutate(treatment = factor(treatment, levels = charlevels)) %>%
    mutate(treatmentNum = as.numeric(treatment)) %>%
    ggplot(aes(x = treatmentNum, y = counts)) +
    geom_boxplot(aes(fill = treatment, color = sex), outlier.shape = NA) +
    #geom_smooth(aes(color = sex)) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    facet_grid(gene~sex, scales = "free") +
    scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8,9),
                       labels = charlevels) +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme_B3() + 
    theme(legend.position = "none",
          strip.text.y = element_text(face = "italic"),
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(subtitle = whichtissue, 
         y = "gene expression (variance stabilized)",
         x = "Parental Care Stage") 
  return(p)
}
